\plaintitle

### 2016-05-20 cscw/papers/2017/labor/trackingWork.tex
fix PineGreen definition
any diffs?

% To make various LaTeX processors do the right thing with page size.
\def\pprw{8.5in}
\def\pprh{11in}
\special{papersize=\pprw,\pprh}
\setlength{\paperwidth}{\pprw}
\setlength{\paperheight}{\pprh}
\setlength{\pdfpagewidth}{\pprw}
\setlength{\pdfpageheight}{\pprh}

\newcommand{\msb}[1]{{\color{PineGreen}[MSB: #1]}}

@@

% create a shortcut to typeset table headings
% \newcommand\tabhead[1]{\small\textbf{#1}}
\bibliography{../../../../references}

@@

The past decade has seen
microtasks, the ``sharing economy'', and other instantiations of on--demand contract work
grow to occupy the fascination of both academic circles and our culture as a whole
\cite{Ross,CrowdsourcingUserStudies,scholz2012digital}.
The research community has identified myriad connections between this emergent form of work
and the historically situated ``piecework'',
\msb{Did the research community really do this? Or is \textbf{your} contribution? I want to understand whether the literature threw around the word as a metaphor, or if they really meant it in the full historical context of the term.}
as well as a number of observations relating to
the frustration workers feel stemming from the management of this work
\cite{turkopticon,dynamo,uberAlgorithm}.
This body of work represents the cornerstones of how we understand crowd workers and on--demand labor more generally.

>>>>

% To make various LaTeX processors do the right thing with page size.
\def\pprw{8.5in}
\def\pprh{11in}
\special{papersize=\pprw,\pprh}
\setlength{\paperwidth}{\pprw}
\setlength{\paperheight}{\pprh}
\setlength{\pdfpagewidth}{\pprw}
\setlength{\pdfpageheight}{\pprh}
\definecolor{PineGreen}{HTML}{008800}
\newcommand{\msb}[1]{{\color{PineGreen}[MSB: #1]}}

@@

% create a shortcut to typeset table headings
% \newcommand\tabhead[1]{\small\textbf{#1}}
\jbibliography{../../../../references}

@@

The past decade has seen
microtasks, the ``sharing economy'', and other instantiations of on--demand contract work
grow to occupy the fascination of both academic circles and our culture as a whole
\cite{Ross,CrowdsourcingUserStudies,scholz2012digital}.
The research community has made connections between this emergent form of work
and the historically situated ``piecework'',
% \msb{Did the research community really do this? Or is \textbf{your} contribution? I want to understand whether the literature threw around the word as a metaphor, or if they really meant it in the full historical context of the term.}
as well as a number of observations relating to
the frustration workers feel stemming from the management of this work
\cite{turkopticon,dynamo,uberAlgorithm}.
With that being said, the connections drawn between
historical piecework and
contemporary crowd work
have largely been used as a high--level tool to contextualize
what otherwise seemed to be a difficult 
% This body of work represents the cornerstones of how we understand crowd workers and on--demand labor more generally.
